Title

### 2018-08-25 thesis/paper/paper.tex
Added "demand" rule to multi value

\subsection{Multi-value (Q21510857)}
The multi-value constraint requires a limited count of constrained statements. Alternatively, it could be said that if the item requires a second statement, the constraint is violated. Pre-processing extracts all items statements and inequality between all item statement properties as usual and the conjunction is \(c = \text{tripleEDB}(S, I, P, V) \wedge \text{unequal}(\text{propertyConstant}, P)\). The predicate require\_second\([2]\) is introduced with the same meaning as require except that it will be applied after a required property has been found:
\begin{equation*}
\begin{split}
\text{require\_second}&(S, \text{propertyConstant}) \leftarrow \\
&\text{next}(Q, R) \wedge \text{next}(R, S) \wedge \text{require}(Q, \text{propertyConstant}) \wedge t \wedge \\
&\text{tripleEDB}(R, I, \text{propertyConstant}, C)
\end{split}
\end{equation*}
\begin{equation*}
\text{require\_second}(S, \text{propertyConstant}) \leftarrow \text{next}(R, S) \wedge \text{require\_second}(R, \text{propertyConstant}) \wedge t
\end{equation*}
A violations would be any last statement requiring a second constrained statement.\\

>>>>

\subsection{Multi-value (Q21510857)}
The multi-value constraint requires a limited count of constrained statements. Alternatively, it could be said that if the item requires a second statement, the constraint is violated. Pre-processing extracts all items statements and inequality between all item statement properties as usual and the conjunction is 
\begin{equation*}
\begin{split}
c = &\text{tripleEDB}(Q, I, \text{propertyConstant}, X) \wedge \\
&\text{tripleEDB}(S, I, P, V) \wedge \text{unequal}(\text{propertyConstant}, P)
\end{split}
\end{equation*}
The predicate require\_second\([2]\) is introduced with the same meaning as require except that it will be applied after a required property has been found:
\begin{equation*}
\begin{split}
\text{require\_second}&(S, \text{propertyConstant}, \text{propertyConstant}) \leftarrow \\
&\text{next}(R, S) \wedge \text{tripleEDB}(R, I, \text{propertyConstant}, C) \wedge \\
&\text{next}(Q, R) \wedge \text{require}(Q, \text{propertyConstant}, \text{propertyConstant})  \wedge c
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{require\_second}&(S, \text{propertyConstant}, \text{propertyConstant}) \leftarrow \text{next}(R, S) \wedge \\
&\text{require\_second}(R, \text{propertyConstant}, \text{propertyConstant}) \wedge c
\end{split}
\end{equation*}
A violations would be any last statement requiring a second constrained statement.\\
